Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-09-29 doc/tfp_2011_final/main.tex
updated KK

There are several implementations of Google's MapReduce in functional
programming languages. But \of{Functory} was just inspired by Google's
MapReduce and is not exactly a MapReduce implementation. The
simplest difference comes from the very fact that \of{Functory} does not
operate on key/value pairs. 
% TODO other difference = absence of data locality
PlasmaMR~\cite{plasma} is an \Ocaml\ implementation of Google's
MapReduce on a distributed file system PlasmaFS. It is able to use
PlasmaFS to its advantage --- the ability of the file system to handle
large files and query functions that implement data locality to
optimize network traffic. However, PlasmaMR does not support 
fault-tolerance which is indispensable in any distributed computing
application.
% The Disco project~\cite{disco} is an implementation of
% Google's MapReduce in Erlang~\cite{erlang}.
Another MapReduce
implementation in \Ocaml\ is Yohann
Padioleau's~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing. Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a more generic API together with fault-tolerance.

@@

Our computing
infrastructure for this experiment consists of 3 machines with 4, 8 and 8 cores
respectively, the master being run on a fourth machine. 
The figure below shows the total time in minutes spent by each prover
for each possible outcome.
\begin{center}
  \begin{tabular}{|r||r|r|r|r|}
    \hline
    prover   & valid & unknown & timeout & failure
    \\\hline\hline
    Alt-ergo & 406.0 & 3.0   &  11400.0 & 0.0       
    \\\hline
    Simplify &  0.5   & 0.4   &  1200.0 & 222.0   
    \\\hline
    Z3       & 80.7   & 0.0   &  1800.0 & 1695.0   
    \\\hline
    CVC3     & 303.0  & 82.7  &  4200.0 & 659.0   
    \\\hline
  \end{tabular}
\end{center}
These figures sum up to more than 6 hours if provers were executed
sequentially. However, using our library and our 3-machine
infrastructure, it completes in 22 minutes and 37 seconds, giving us a
speedup of more than 16$\times$. We are still far away from the ideal
ratio of 20$\times$ (we are using 20 cores), since some provers are
allocating a lot of memory and time spent in system calls is not
accounted for in the total observed time. However, a ratio of
16$\times$ is already a significant improvement for our day-to-day
experiments. Further a large parallelizable computation could be
distributed by just adding 3-4 lines of code (to just specify the module
to be used and the tasks) which is an important user-friendly feature
of the library.

>>>>

There are several implementations of Google's MapReduce in functional
programming languages. But \of{Functory} was just inspired by Google's
MapReduce and is not exactly a MapReduce implementation. The
simplest difference comes from the very fact that \of{Functory} does not
operate on key/value pairs. 
% TODO other difference = absence of data locality
PlasmaMR~\cite{plasma} is an \Ocaml\ implementation of Google's
MapReduce on a distributed file system PlasmaFS. It is able to use
PlasmaFS to its advantage --- the ability of the file system to handle
large files and query functions that implement data locality to
optimize network traffic. However, PlasmaMR does not support 
fault-tolerance which is indispensable in any distributed computing
application.
% The Disco project~\cite{disco} is an implementation of
% Google's MapReduce in Erlang~\cite{erlang}.
Another MapReduce
implementation in \Ocaml\ is Yohann
Padioleau's~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing. Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a more generic API together with fault-tolerance. We
feel that an indispensible need for any distributed computing library
is fault-tolerance, and using a homemade protocol enables us to
tune our implementation to our needs of fault-tolerance.

@@

Our computing
infrastructure for this experiment consists of 3 machines with 4, 8 and 8 cores
respectively, the master being run on a fourth machine. 
The figure below shows the total time in minutes spent by each prover
for each possible outcome.
\begin{center}
  \begin{tabular}{|r||r|r|r|r|}
    \hline
    prover   & valid & unknown & timeout & failure
    \\\hline\hline
    Alt-ergo & 406.0 & 3.0   &  11400.0 & 0.0       
    \\\hline
    Simplify &  0.5   & 0.4   &  1200.0 & 222.0   
    \\\hline
    Z3       & 80.7   & 0.0   &  1800.0 & 1695.0   
    \\\hline
    CVC3     & 303.0  & 82.7  &  4200.0 & 659.0   
    \\\hline
  \end{tabular}
\end{center}

These figures sum up to more than 6 hours if provers were executed
sequentially. However, using our library and our 3-machine
infrastructure, it completes in 22 minutes and 37 seconds, giving us a
speedup of more than 16$\times$. We are still far away from the ideal
ratio of 20$\times$ (we are using 20 cores), since some provers are
allocating a lot of memory and time spent in system calls is not
accounted for in the total observed time. However, a ratio of
16$\times$ is already a significant improvement for our day-to-day
experiments. Further a large parallelizable computation could be
distributed by just adding 3-4 lines of code (to just specify the
module to be used and the tasks) which is an important user-friendly
feature of the library. Further we assume files available over
NFS. Intelligent distribution of data over a network is in itself an
area of research which is beyond the scope of our work.
